--- 
title: "Excel for General Chemistry"
author: "David Hall, David Liu, and Jessica D'eon"
date: "Book last built on `r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [book.bib, packages.bib]
csl: american-chemical-society.csl
link-citations: yes
github-repo:  UofTChem-Teaching/excel4chem 
description: "This is a prelimary book aimed to help undergraduate chemistry students learn Micorsoft Excel"
---

```{r, setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, error = FALSE)
```

```{r}

library(tidyverse)
```

# Preface {-}

Hello and Welcome the University of Toronto's **First Year Chemistry Online Excel Resource**!

This online resource was created to help students succeed in first year chemistry and beyond. We hope you find it useful! 

This book will is broken up into five sections: 

**[Introduction]**
Many examples in this resource use air quality data from Environment and Climate Change Canada’s [National Air Pollution Surveillance (NAPS) program](https://www.canada.ca/en/environment-climate-change/services/air-pollution/monitoring-networks-data/national-air-pollution-program.html). This section provides the necessary background information on the chemistry of air quality so that you understand the *why* of many of the Excel manipulations discussed. If you are accessing this resource for a class this introductory material is often provided on Quercus and this section is not relevant.

**[Getting Setup for Success]**
This section takes you through how to access Excel and Word as a U of T student, how to organize and backup your files and how to create professional documents. 

**[Data Wrangling]**
This section takes you through the process of data analysis from opening your file, through properly formatting the cells, to cleaning the data to produce a dataset that is ready for further analysis.

**[Math, Stats, and Programming]**
This section explores how to input mathematical formulas into Excel and many useful functions.

**[Data Visualization ]**
This section explores typical ways of visualizing data in the chemistry lab and how to alter and adjust these plots.

## Providing Feedback {-}

If you notice an error, mistake or if you have suggestions for adding features or improving the book, please reach out to us or flag an issue on [GitHub](https://github.com/UofTChem-Teaching/excel4chem).

  - [Dave](https://sites.chem.utoronto.ca/penglab/content/people) at [davidross.hall@mail.utoronto.ca](davidross.hall@mail.utoronto.ca)
  - [Jessica D'eon](https://www.chemistry.utoronto.ca/people/directories/all-faculty/jessica-deon) at [jessica.deon@utoronto.ca](jessica.deon@utoronto.ca)

## Authors {-}
  
  - [David Hall](https://sites.chem.utoronto.ca/penglab/content/people) 
  - [David Liu](https://www.cs.toronto.edu/~david/)
  - [Jessica D'eon](https://www.chemistry.utoronto.ca/people/directories/all-faculty/jessica-deon)
  
## Acknowlegements {-}

Additionally, we would like to thank ....