--- 
title: "Excel for General Chemistry"
author: "David Hall, David Liu, and Jessica D'eon"
date: "Book last built on `r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [book.bib, packages.bib]
csl: american-chemical-society.csl
link-citations: yes
github-repo:  UofTChem-Teaching/excel4chem 
description: "This is a prelimary book aimed to help undergraduate chemistry students learn Micorsoft Excel"
---

```{r, setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, error = FALSE)
```

```{r}
library(DT)
library(tidyverse)
```

# Welcome! {-}

**Hello and Welcome the University of Toronto's First Year Chemistry Online Excel Resource!!**

This resource was created to provide students at the University of Toronto with the Excel and Word skills to succeed in first year chemistry and beyond. We hope you find it useful! This book is broken up into the following five sections: 

**[Introduction]**
Many examples in this resource use air quality data from Environment and Climate Change Canada’s [National Air Pollution Surveillance (NAPS) program](https://www.canada.ca/en/environment-climate-change/services/air-pollution/monitoring-networks-data/national-air-pollution-program.html). This section provides the necessary background information on the chemistry of air quality so that you understand the *why* of many of the Excel manipulations discussed. If you are accessing this resource for a class this introductory material is often provided on Quercus and this section is not relevant.

**[Getting Setup for Success]**
This section takes you through how to access Excel and Word as a U of T student, how to organize and backup your files, and how to create professional documents. 

**[Data Wrangling]**
This section takes you through the process of data analysis from opening your file, through properly formatting cells, to cleaning a dataset to produce data that is ready for further analysis.

**[Math, Stats, and Programming]**
This section explores how to input mathematical formulas into Excel and will take you through the execution of many useful functions.

**[Data Visualization ]**
This section explores typical ways of visualizing data in the chemistry lab and how to alter and adjust these plots.

## Providing Feedback {-}

If you notice a mistake or if you have any suggestions for improving this resource, please submit your feedback using this [MS form](https://forms.office.com/Pages/ResponsePage.aspx?id=JsKqeAMvTUuQN7RtVsVSEGHZDOek28RImgdKIDiK0wdUMVVISEVPWllTNjZPVjg3RlZHQTkzQTZXNC4u).
